Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-06-07 paper-v1.tex
Update

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of the smart contract functionality introduced by Ethereum. 
Besides a growing number of applications ranging from business, healthcare, music industry, government, to cite a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices. In particular, a 'blockchainefied science'\cite{BlockchainforScience} could 'increase value and reduce waste’\cite{ReducingWaste-Lancet}, by disclosing the research cycle to scientific assessment way before the final publication step and therefore help fixing the current reproducibility crisis in science.
"blockchain would make much larger parts of the research cycle open to scientific self-correction. This bears the potential to be a new approach to the current reproducibility crisis in science, and could ‘reduce waste and make more research results true’. Beyond that, blockchain could be used to reduce overhead and accelerate the scientific process and incentivise true innovation."

@@

"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers.Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9. Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."

@@

\subsection{Related work}
Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like imapct factor h-index.
In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
\emph{DEIP}
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews.
\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
\emph{ReviewCoin}
\emph{I8X Platform}
A more comprehensive reform of academic endorsement has been proposed in the manifesto ‘Towards Open Science:The Case for a Decentralized Autonomous Endorsement System11’, published anonymously.The author(s) propose a new academic endorsement system that is not based on current journal publication practices which are argued to be expensive, slow, disregard non-traditional output and negative results, and which give too much power to editors and publishers. Built on the blockchain, the Academic Endorsement System (AES) is based on a new form of currency, coined academic endorsement points (AEP), which can be used by scientists to reward scientific work that is worthy of endorsement. Moreover, the amount of AEP credited to a scientist is based on the AEP received for previous work. Researchers whose output has been endorsed to a high degree will have a larger influence in the community. Any kind of research output could be endorsed, for example blog posts, data sets, software etc.Another advantage is that this system would be faster than the time it takes for citation metrics to accrue.
The startup Matryx.ai13 aims to transform the nature of research collaboration itself. Its initiators claim that one of the problems with current scientific practices is its incentive structure. Scientific awards, for example, are based on competition rather than on collaboration, despite the fact that new ideas are usually collaborative in nature. Moreover, different researchers and research groups are often working on the same problems, wasting, as they claim on their website,‘brain power’, time and money. Matryx intends to provide a platform enabling and incentivising research collaboration while discouraging solitary and siloed research. On Matryx, a research project starts when users set a bounty on a problem that they want the community to solve. Contributors solve these problems by working with each other on the platform.The collaboration is tracked through the blockchain thus ensuring contributors are credited appropriately when the problem is solved. In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.

@@

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors and that . We imagine a final paper originating from the peer-review process as a complex system that emerges from the product of interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name hints at the ant colony as a model of self-organization in which all micro-contributions of the individuals add up to complex behaviour.
A previous version of this paper can be found here \cite{AntsReview}, as a proposal submitted for the ETH Turin 2020 Hackathon.
and it’s design and attempt of implementation are exposed in the following section.
Here I expose the main traits/features of AR
\begin{itemize}
\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. this means the platform acts like a version control system where commit are permanent and hashed 
\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports 
\item incentivisation: via symbolic and material recognition of the performed work. tokens and bounty
\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
\end{itemize}
crowdfunding schemes leveraged by blockchain technology
In the following sessions we describe the architecture of the system and its building blocks
AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network[ref], ERC20[ref], AZTEC Protocol[ref], IPFS[ref], Proof of Existence[ref], ...

@@

\begin{enumerate}
    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
    \item The paper is accepted by the community for revision in its whatever format.
    \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community with Quadratic Voting.
    \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit. It will also fuel ethical behaviour.

@@

\section{Conclusion}
In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.

>>>>

\begin{document}
%
\title{Ants-Review: A Protocol For Open Anonymous Peer-Reviews}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Correspondent author: bianca.trovo@alumni.unitn.it} \and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}}
%
\authorrunning{B. Trovò et N. Massari}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, 75005 Paris, France \and
Neurospin research center, CEA/SAC/DSV/I2BM, 91191 Gif-sur-Yvette, France
\email{bianca.trovo@alumni.unitn.it}\\
\and
Alma Mater Politecnico di Torino, 10129 Turin, Italy\and
Independent Blockchain Engineer, London, UK \\
\email{nazzareno@nazzarenomassari.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Peer-review is a necessary and essential quality control step for scientific publications. However, the process, which is very costly in terms of time investment, not only is not remunerated but it’s also not recognized by the academic community as a relevant scientific output for a researcher. Therefore, scientific dissemination is affected. Here, to solve this issue we propose a blockchain-based incentive protocol that rewards scientists also for their contributions to other scientists’ work and that builds up a reputational system. We designed a basic Bounty-like contract called AntsReview that allows any author to issue a call for peer-reviewing their scientific publication. If requirements are met, peer-reviews will be audited by an external editor and payed by the Issuer. To promote ethical behaviour the system will implement a quadratic funding on AntsReview.
\keywords{Blockchain  \and Open Science \and Peer-review \and Incentivization.}
\end{abstract}
%
%
\section{Introduction}
From its birth in 2008 as a distributed ledger for the peer-to-peer electronic cash system 'Bitcoin' \cite{Bitcoin}, blockchain technology has spread far beyond the sole cryptocurrency domain, in particular after the implementation of a general purpose smart contract functionality introduced by Ethereum. 
Besides a growing number of applications ranging from business, healthcare, music industry, government, identity to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a 'game changer' in outdated and broken scientific practices and leading towards Open Science \cite{AES}. In particular, a 'blockchainified science'\cite{BlockchainforScience} could 'reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step the research cycle to 'scientific self-correction' way before the final publication step and therefore help fixing the current reproducibility crisis in science. Scholars have pointed out how the intrinsic characteristics of blockchain technology (decentralization, for which there are no trusted third parties; cryptographic hashing, that creates a digital footprint able to keep a 'trail of research';  
to prevent vs publication bias (reporting only positive results) or p-hacking or ex-post-facto hypothesizing (changing the hypothesis after having looked into the data)

@@

"Peer review In recent years a lot of attention has been given to fundamental problems associated with the peer review process which lies at the heart of scholarly communication5,6,7.The perceived problems are multiple.There is a lack of visibility and recognition for reviewers, with their review work remaining largely unnoticed.Together, the increased number of manuscripts submitted to journals, and a subsequent need for more reviewers, leads to an increasing difficulty in finding suitable reviewers. Additionally, there is a perceived bias against women in the review process8.There are also cases of review manipulation, sometimes involving identity fraud which forced publishers to retract articles9. Overall, the review process is considered opaque and expensive, slowing down the speed of scientific discovery and progress."

@@

\subsection{Related work}
Credit for peer review is not a new thing: mostly journals handled it so far with virtual 'badges', certificates of performance, citation in annual editorials but none of these is standardized in a way that has a weight for funders world ranking bodies institutions like impact factor h-index.
In relation to security issues \emph{CryptSubmit} \emph{MaRSChain}
\emph{Crossref} primary DOI provider, announced that review reports could be now registered as part of their services
\emph{Publons} provides a way to keep track of the reviews records and integrate them into academic profiles such as ORCID
ScienceOpen
\emph{DEIP}
Rubriq provides independent and standardized peer review that can be accepted and shared across all types of journals and distribution systems. Now absorbed by Research Square.
\emph{Peerage of Science} that provides a journal-independent free service for scientific peer review and publishing. The interesting feature is that it provides also a peer-review of the reviews.
\emph{Blockchain for Peer Review,}pilot project sponsored by Digital Science and Katalysis, aims at developing a protocol for storing peer reviews submitted by publishers on a blockchain such that review process can be independently verified and review info is fed to ORCID researcher profiles []
\emph{ReviewCoin}
\emph{I8X Platform}
A more comprehensive reform of academic endorsement has been proposed in the manifesto ‘Towards Open Science:The Case for a Decentralized Autonomous Endorsement System11’, published anonymously.The author(s) propose a new academic endorsement system that is not based on current journal publication practices which are argued to be expensive, slow, disregard non-traditional output and negative results, and which give too much power to editors and publishers. Built on the blockchain, the Academic Endorsement System (AES) is based on a new form of currency, coined academic endorsement points (AEP), which can be used by scientists to reward scientific work that is worthy of endorsement. Moreover, the amount of AEP credited to a scientist is based on the AEP received for previous work. Researchers whose output has been endorsed to a high degree will have a larger influence in the community. Any kind of research output could be endorsed, for example blog posts, data sets, software etc.Another advantage is that this system would be faster than the time it takes for citation metrics to accrue.
The startup Matryx.ai13 aims to transform the nature of research collaboration itself. Its initiators claim that one of the problems with current scientific practices is its incentive structure. Scientific awards, for example, are based on competition rather than on collaboration, despite the fact that new ideas are usually collaborative in nature. Moreover, different researchers and research groups are often working on the same problems, wasting, as they claim on their website,‘brain power’, time and money. Matryx intends to provide a platform enabling and incentivising research collaboration while discouraging solitary and siloed research. On Matryx, a research project starts when users set a bounty on a problem that they want the community to solve. Contributors solve these problems by working with each other on the platform.The collaboration is tracked through the blockchain thus ensuring contributors are credited appropriately when the problem is solved. In principle, everyone can contribute in the collaboration: scientists, PhD students and even enthusiastic amateurs.

@@

\section{System concept}
In this paper we propose Ants-Review, a new incentivisation mechanism built on a distributed platform that issues open peer-reviews to validate scientific papers while preserving the anonymity of its contributors. We imagine a final paper originating from the peer-review process as a complex system that emerges from the interactions between the authors and the reviewers, a whole that is more than the sum of its parts. Therefore, the name evokes an ant colony as a self-organising organism in which all micro-contributions of the individuals emerge into complex behaviour.
A previous version of this paper can be found here \cite{AntsReview}, as a proposal submitted for the ETH Turin 2020 Hackathon.
and its design and attempt of implementation are exposed in the following section.
Here we expose the main traits/features of AR
\begin{itemize}
\item accountability: both for recognition and for security vs fraud abuse etc we need to be able to track back the identities of the contributors to a peer-review to make sure there are no conflict of interest. this means the platform acts like a version control system where commit are permanent and hashed 
\item transparency of the records: all reviews should be open access to the community to prevent waste of knowledge and disrupt the secretive system of black boxes of peer reviews in journals that centralize all the reports 
\item incentivisation: via symbolic and material recognition of the performed work. reputation and bounties
\item inclusiveness via gamification: all the community is involved in the process - no selection process feeling of belonging -- quadratic voting and share of the stake
\end{itemize}
crowdfunding schemes leveraged by blockchain technology
In the following sections we describe the architecture of the system and its building blocks
AntsReview [Fig.\ref{fig:contracts}] is a distributed peer-review system which synthesizes successful ideas from previous systems including The Bounty Network \cite{Bounty}, ERC-20 \cite{ERC20}, AZTEC Protocol \cite{AZTEC}, IPFS \cite{IPFS}, Proof of Existence \cite{TimeStamp-Haber}, ...

@@

\begin{enumerate}
    \item The author submits a manuscript to the pre-print service or to an hypothetical AntsReview platform).
    \item The paper is accepted by the community for revision in its whatever format.
    \item The author issues a bounty (\emph{bounty issuance}) for the paper review. Fulfillment rules are set in a smart-contract.
    \item (footnote?) the bounty prize could come by a community stake that participates in the peer-review process either as a reviewer or as a reviewer checker.
    \item Reviews fulfilling the smart-contract requirements are validated by the AntsReview community/contributors.
    \item When the reviews are accepted (\emph{bounty fulfillment}), reviewers awarded a token called \emph{ANT}.
    \item Not all reviews will have the same quality and depth. However, each of them might bring up one or more relevant contribution for the sake of improving the manuscript. In order to redistribute the bounty in a fair manner across reviewers, reviews will be voted by the community via Quadratic Voting.
    \item In order to incentive 'fair play' also the review checkers who vote for the best quality reviews will share the final prize from the bounty. Since it's in their own interest to 'bet' on a good review, this gamed system will discourage internal dynamics prompt to favour specific members of the community beyond real personal merit. It will also fuel ethical behaviour.

@@

\section{Conclusion}
In this paper we addressed a crucial problem within scholarly academic communication: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possible directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.
